Tropical Mathematics for the Lambda Calculus

### 2023-01-14 section3C.tex
Mini-commit
Ho aggiustato minime cose, ed ho elencato alcuni punti da dire nelle conclusions

\begin{theorem}\label{thm:modelsTaylor}
 In $\LREL_!$ equipped with $D$, all morphisms can be Taylor expanded, i.e.\ in $\LREL_!$ we have the following equality:
 \[
  \RM{eval}^{X,Y}\circ_!\langle t,s\rangle =
  \inf\limits_{n\in\N}
  \set{((\dots((\Lambda^- t)\star s)\star \dots)\star s)\circ_! \langle \RM{id},\infty \rangle}.
 \]
 for all $t\in\HOM{\LREL_!}{Z}{X\multimap Y}$, $s\in\HOM{\LREL_!}{Z}{X}$.
\end{theorem}
Here, $\Lambda^-:\HOM{\LREL}{!Z}{X\multimap Y}\to \HOM{\LREL}{!(Z+X)}{Y}$ is the uncarry operator and $\star:\HOM{\LREL}{!(Z+X)}{Y}\times\HOM{\LREL}{!Z}{X}\to \HOM{\LREL}{!(Z+X)}{Y}$ is an operator corresponding to the syntactical \emph{differential substitution}.
\begin{proof}
 Che ci scriviamo ??
\end{proof}

>>>>

\begin{theorem}\label{thm:modelsTaylor}
 In $\LREL_!$ equipped with $D$, all morphisms can be Taylor expanded, i.e.\ in $\LREL_!$ we have the following equality:
 \[
  \RM{eval}^{X,Y}\circ_!\langle t,s\rangle =
  \inf\limits_{n\in\N}
  \set{((\dots((\Lambda^- t)\star s)\star \dots)\star s)\circ_! \langle \RM{id},\infty \rangle}.
 \]
 for all $t\in\HOM{\LREL_!}{Z}{X\multimap Y}$, $s\in\HOM{\LREL_!}{Z}{X}$.
\end{theorem}
Here, $\Lambda^-:\HOM{\LREL}{!Z}{X\multimap Y}\to \HOM{\LREL}{!(Z+X)}{Y}$ is the uncarry operator and $\star:\HOM{\LREL}{!(Z+X)}{Y}\times\HOM{\LREL}{!Z}{X}\to \HOM{\LREL}{!(Z+X)}{Y}$ is an operator corresponding to the syntactical \emph{differential substitution} of $\STDLC$.
\begin{proof}
 {\color{red}(Che ci scriviamo ??}
\end{proof}

### 2023-01-14 section3intro.tex
Mini-commit
Ho aggiustato minime cose, ed ho elencato alcuni punti da dire nelle conclusions

In the remainder of this section we will see how tropical linear algebra -- expressed as $\LREL$ -- gives rise to denotational models of computation -- expressed as \lamcalc.

>>>>

In the remainder of this section we will see how tropical linear algebra -- expressed as $\LREL$ -- gives rise to denotational models of computation -- expressed as variants of the \lamcalc.

### 2023-01-14 section4.tex
Mini-commit
Ho aggiustato minime cose, ed ho elencato alcuni punti da dire nelle conclusions

\begin{proposition}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv^Y$ is non-decreasing and concave, w.r.t.\ the pointwise order.
\end{proposition}

@@

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 The result follows after proving that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

@@

@@

@@

\begin{proposition}
  Tropical Laurent series $\Lawv^X\to\Lawv^Y$ are Scott-continuous on $\BB R_{>0}$, w.r.t.\ the cone orders on the domain and codomain.
\end{proposition}

>>>>

\begin{proposition}\label{prop:nondecr+conc}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv^Y$ is non-decreasing and concave, w.r.t.\ the pointwise order.
\end{proposition}

@@

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 The result follows after proving that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

@@

We believe that a variant of such result holds in $\Lawv^X$ for $X$ finite.
We do not know what happens if $X$ is infinite.

@@

Proposition~\ref{prop:nondecr+conc} and Theorem~\ref{thm:cont} immediately entail:
\begin{corollary}\label{cor:TLSlocLip}
 Tropical Laurent series $\Lawv^X\to\Lawv$ are locally Lipschitz on on $\BB R_{>0}$.
\end{corollary}

@@

\begin{proposition}
  Tropical Laurent series $\Lawv^X\to\Lawv^Y$ are Scott-continuous on $\BB R_{>0}^X$, w.r.t.\ the cone orders on the domain and codomain.
\end{proposition}
